DOpElib:\\ Differential Equations and Optimization Environment

### 2013-12-12 Examples/OPT/StatPDE/Example6/content.tex
Doku anpassung

{\textcolor{red}{
The Problem is similar to that of {\tt OPT/StatPDE/Example1} except for the box control constraints.
The implementation of these constraints is taken care of in the main file
(where we add a constrained description \texttt{lcc}) and in the
\texttt{localconstraints.h} file. This files serves to implement the actual constraints. 
In this example, we introduce the handling of \textit{local} constraints
whereas the mixture of local and \textit{global} constraints will be discussed
in the next Example \ref{OPT_Stat_MBB-Beam}. 
%
First, we implement the upper and lower control bounds in 
\texttt{localconstraints.h}, i.e,
\[
q_{min} \leq q \leq q_{max}.
\]
with $q_{min} = -500$ and $q_{max} = 500$.
%
Second, the \texttt{lcc} vector describes the meaning and the applicability of
these constraints. Further information can be found
in \texttt{basic/constraints.h}. We give here the necessary information for
the 
present example. We initialize \texttt{lcc(1)}, i.e., we have 1 control block.
Then, this block is given the constant size $2$ (in the case of more than one 
control block, each block would be given a size of $2$). The first
entry \texttt{lcc[0][\textcolor{red}{0}] = 1} tells 
you how many local entries in the present block are locally constrained, here 
it is $1$ local entry. The second entry \texttt{lcc[0][\textcolor{red}{1}] =
2}, determines the number of constraints on this local entry. Here, we impose 
a lower and an upper bound, i.e., we give 2 constraints.
}

>>>>

The Problem is similar to that of {\tt OPT/StatPDE/Example1} except for the box 
control constraints.
The implementation of these constraints is taken care of in the main file
(where we add a constrained description \texttt{lcc}) and in the
\texttt{localconstraints.h} file. This files serves to implement the actual constraints.

In this example, we introduce the handling of \textit{local} constraints
whereas the mixture of local and \textit{global} constraints will be discussed
in the Example \ref{OPT_Stat_MBB-Beam}. 
%
First, we implement the upper and lower control bounds in 
\texttt{localconstraints.h}, i.e,
\[
q_{\min} \leq q \leq q_{\max}.
\]
with $q_{\min} = -500$ and $q_{\max} = 500$.
The constraints are `local', by which we mean the constraints are imposed 
on the nodal values of the control vector. Thus, in the constraint 
description \texttt{localconstraints.h},
these vectors are manipulated directly without additional integration. We 
note that the constraints need to be written such, that a feasible control
generates non positive entried, i.e., we 
calculate the vector
\[
 \mathcal C(q) = \begin{pmatrix}
   q_{\min} - q\\q-q_{\max}
 \end{pmatrix}.
 \]
%
Second, the \texttt{lcc} vector is used to describe the amount of unknowns that 
need to be reserved to store the constraints, and, eventually, corresponding 
Lagrange multipliers. 
Further information can be found in \texttt{basic/constraints.h}. 
In our example, we have only one block in the control (The control is stored in 
a \texttt{deal.II::BlockVector}). Hence, the \texttt{lcc} vector has a length of 
one. 
The only entry \texttt{lcc[0]} is a vector of size two (in the case of more than one 
control block, each block would be given a size of $2$). 
Each of the two entries has a specific meaning. 
The first entry \texttt{lcc[0][\textcolor{red}{0}] = 1} tells 
you how many local entries in the present block are locally constrained, here 
it is one local entry. ({\em Note that this entry will typically be one. 
it is not one  would be if we have constraints of the type $q_{i} + q_{i+1} \le 1$ for each 
even $i$, or similar combinations of multiple entries in the control vector.})

The second entry \texttt{lcc[0][\textcolor{red}{1}] = 2}, determines the number of 
constraints on this local entry. Here, we impose 
a lower and an upper bound, i.e., we give 2 constraints.
This information tells the SpaceTimeHandler, that the vector 
$\mathcal C(q)$ needs exactely twice the amount of unknowns as the vector $q$.
In general, the space needed for $\mathcal C(q)$ is given as 
\[
\frac{\text{\texttt{lcc[0][1]}}}{\text{\texttt{lcc[0][0]}}}
\]
times the unknowns for the control.

### 2013-12-12 Examples/OPT/StatPDE/Example7/content.tex
typo
Doku anpassung

\subsubsection{Program description}
\textcolor{red}{
In addition to the previous Example \ref{OPT_Stat_MBB-Beam}, we consider now 
in addition 1 global constraint, which is realized by setting $1$ in the 
second argument of \texttt{constraints(lcc, 1)}. 
We use 
\texttt{localconstraints.h} and \texttt{localconstraintaccessor.h} to impose 
all constraints. First, we have again one control block with a lower and 
an upper bound, 
\[
\rho_{min} \leq q \leq \rho_{max}
\]
with $\rho_{min} = 10^{-4}$ and $\rho_{max} = 1$ ($\rho$ denotes the density
of the material). These are implemented in \texttt{localconstraintaccessor.h}.
The global constraint is the maximum volume of the material,
which should remain constant with the value $0.54$. Its implementation is 
provided in \texttt{localconstraints.h}.
}

>>>>

\subsubsection{Program description}
In addition to the previous Example \ref{OPT_Stat_Box_controlconstraints_SNOPT}, 
we consider now in addition one global constraint. To calculate the correct 
storrage needed we use the 
second argument of \texttt{constraints(lcc, 1)}, which is now one.

We use 
\texttt{localconstraints.h} and \texttt{localconstraintaccessor.h} to impose 
all constraints. First, we have again one control block with a lower and 
an upper bound, 
\[
\rho_{min} \leq q \leq \rho_{max}
\]
with $\rho_{min} = 10^{-4}$ and $\rho_{max} = 1$ ($\rho$ denotes the density
of the material). These are implemented in \texttt{localconstraintaccessor.h}.
The global constraint is the maximum volume of the material,
which should remain constant with the value $0.5$. Its implementation is 
provided in \texttt{localconstraints.h} where the global constraint is handled as 
a functional, which again is normalized to be nonpositive if the control is feasible.
